\LARGE \bf Thymio, an example of open source hardware robot \\ for formal education

### 2016-03-31 paper_ram.tex
changes pour commentaires de steph

\subsection{Multi-age and Gender-neutral Feature Set}

@@

\subsection{Short time to demo}
\label{sec:behaviors}

@@

Thymio runs the Aseba open-source programming environment~\cite{aseba}.
Aseba is designed to enable novices to program robots easily.
On the robot side, it provides a lightweight virtual machine that runs on microcontrollers like the PIC24F.
A virtual machine allows instantaneous upload and safe execution of code.
On the desktop side, Aseba provides an IDE which allows to program in a purely graphical mode, or using a scripting language (see Figure~\ref{fig:aseba-studio}) or in a mixed way, assembling code in a graphical way using the blockly environment\footnote{\url{https://developers.google.com/blockly/}}.

@@

The IDE integrates a help documentation\footnote{currently English, French, and German}.
In addition, the wiki pages of the project provide tutorials on programming with Thymio and a detailed description of the programming interface.
%The latter was designed with consistency in mind: variables and functions are available in namespaces and similar features (such as the different LEDs) are accessed the same way.
%It also provides native functions for school-level mathematics such as vector operations, trigonometry, statistics and functions such as sorting and random.

>>>>

\subsection{Multi-age and Gender-neutral Feature Set}
\label{sec:multi}

@@

\subsection{Fast access to robotics behaviors}
\label{sec:behaviors}

@@

Thymio runs the Aseba open-source programming environment~\cite{aseba}.
Aseba is designed to enable novices to program robots easily.
On the robot side, it provides a lightweight virtual machine that runs on microcontrollers like the PIC24F.
A virtual machine allows instantaneous upload and safe execution of code.
On the desktop side, Aseba provides an IDE which allows to program in a purely graphical mode (called VPL), or using a scripting language (see Figure~\ref{fig:aseba-studio}) or in a mixed way, assembling code in a graphical way using the blockly environment\footnote{\url{https://developers.google.com/blockly/}}.
This allows the IDE to match with the multi-age goal described in section~\ref{sec:multi}.

@@

The IDE integrates real-time feedback both graphically under VPL~\cite{Magnenat2015} and displaying variables or graphs in the text mode.
The IDE also provides a help documentation\footnote{currently English, French, and German}.
In addition, the wiki pages of the project provide tutorials on programming with Thymio and a detailed description of the programming interface.
%The latter was designed with consistency in mind: variables and functions are available in namespaces and similar features (such as the different LEDs) are accessed the same way.
%It also provides native functions for school-level mathematics such as vector operations, trigonometry, statistics and functions such as sorting and random.
